The Weakly Nonlinear Saturation of the Magnetorotational Instability

### 2014-09-19 paper/mri_paper.tex
appendix stuff

\usepackage[colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{gensymb}
\usepackage{amsmath}
\usepackage{color}
%\usepackage{appendix}
\usepackage[titletoc,title]{appendix}

@@

The multiscale expansion of the operators and the perturbation series expansion of the fluid quantities combine to make the expansion of the nonlinear vector $\mathbf{N}$ expansive, and we relegate the expansion to Appendix (REF). $\mathbf{N}$ becomes

\beq
\mathbf{N} = \epsilon^2\mathbf{N_2} \, + \, \epsilon^3\mathbf{N_3} \, + \, \mathcal{O}(\epsilon^4),
\eeq

@@

\newpage
\begin{appendices}
\begin{widetext}
\section*{Appendix A.}

@@

Second order nonlinear terms: \\

@@

Third order nonlinear terms: \\

@@

\end{widetext}
\end{appendices}

>>>>

\usepackage[colorlinks,urlcolor=blue,citecolor=blue,linkcolor=blue]{hyperref}
\usepackage{gensymb}
\usepackage{amsmath}
\usepackage{color}
%\usepackage{appendix}
\usepackage[titletoc,title]{appendix}
\usepackage{cleveref}

@@

The multiscale expansion of the operators and the perturbation series expansion of the fluid quantities combine to make the expansion of the nonlinear vector $\mathbf{N}$ expansive, and we relegate the expansion to Appendix \ref{app:appendix_nonlinear}. $\mathbf{N}$ becomes

\beq
\mathbf{N} = \epsilon^2\mathbf{N_2} \, + \, \epsilon^3\mathbf{N_3} \, + \, \mathcal{O}(\epsilon^4).
\eeq

@@

\newpage
\begin{subappendices}
\begin{widetext}
\section*{Appendix A. Nonlinear term expansion}\label{app:appendix_nonlinear}

@@

$\mathbf{N_2}$ and $\mathbf{N_3}$ expand to become

\beq
\mathbf{N_3} = \alpha^3 \mathbb{N}_{33} e^{i 3 k_c z} + \alpha\partial_Z\alpha \mathbb{N}_{32} e^{i 2 k_c z} + \alpha\left|\alpha\right|^2 \mathbb{N}_{31} e^{i k_c z} + \alpha \partial_Z  \beta \mathbb{\widetilde{N}}_{31} e^{i k_c z} + \alpha^*\partial_Z \alpha \mathbb{N}_{30} + c.c.
\eeq

The second order nonlinear terms are \\

@@

and the third order nonlinear terms become \\

@@

\end{widetext}
\end{subappendices}
